% Documentation: https://ctan.math.washington.edu/tex-archive/macros/latex/contrib/moderncv/manual/moderncv_userguide.pdf
\documentclass[11pt,a4paper,sans]{moderncv}

% ModernCV theme
\moderncvstyle{classic}
\moderncvcolor{blue}

% Adjust page margins
\usepackage[scale=0.75]{geometry}
\usepackage{amsmath}
\usepackage{hyperref}
\setlength{\parskip}{0.5em}

% Personal data
\name{Spyridon Chrysovalantis}{Zervos}
\title{
Postgraduate Student at Computer Science Department, University of Crete \newline
Research Assistant at Information Systems Laboratory, ICS-FORTH, \newline
Member of the INGENIUM Student Board for the University of Crete
}
\address{Voutes Campus, University of Crete}{70013 Heraklion, Greece}
\phone[mobile]{+30 6975908045}
\email{zervosvalantis@gmail.com}
\social[github]{\underline{VZervos}}
\social[linkedin]{\underline{VZervos}} 

%-------------------------------------------------------------------------------
% Content
%-------------------------------------------------------------------------------
\begin{document}

\makecvtitle

%-------------------------------------------------------------------------------
% Short Bio
%-------------------------------------------------------------------------------
\label{sec:ShortBio}
\section{Short Bio}
I am currently a postgraduate student at the Computer Science Department of the University of Crete (CSD, UoC), which has been ranked first in Greece in Informatics/Computer Science for 2025. I hold a BSc from the same department with a grade of 9.57/10, \hyperref[HA:KARAMITZOU2025]{ranking second among the students of my year of admission in the school}. \\

Since my second year of undergraduate studies, I have been an undergraduate scholar at FORTH-ICS. I have worked on the technological upgrade of the openABEKT system, commissioned by the National Documentation and Electronic Content Centre of Greece (EKT). Over the past two years, I have conducted research on both national and international research projects at the Information Systems Laboratory (ISL) of ICS-FORTH. Currently, I am a graduate researcher working on the research projects of the laboratory as well as on my master's thesis. \\

I have been awarded two (3) scholarships, along with four (6) other distinctions and awards, including ranking 8th nationwide for the HIAS scholarship (2024) and placing in the top 13\% of applicants for EPFL worldwide (2025). Additionally, I held a \hyperref[HA:DEPROFOIT]{distinguished Undergraduate Teaching Assistant position in my department}, and nowadays, I am a member of the INGENIUM Student Board, representative of the University of Crete. \\

My primary research interests include Web and Semantic Data Management, Natural Language Processing (NLP), full-stack programming, and the integration of these fields with Large Language Models (LLMs). \\ \\

%-------------------------------------------------------------------------------
% Education
%-------------------------------------------------------------------------------
\label{sec:Education}
\section{Education}

\label{ED:MSC}
\cvitem{MSc Candidate 2025-Present}{
  \textbf{Currently pursuing Master\'s Degree in Computer Science}\newline
  School: \textbf{Computer Science Department, University of Crete (CSD, UoC)}\newline
}

\label{ED:BSC}
\cvitem{BSc 2021-2025}{
  \textbf{Bachelor Degree in Computer Science}\newline
  School: \textbf{Computer Science Department, University of Crete (CSD, UoC)}\newline
  Grade: \textbf{9.57/10} \hyperref[HA:KARAMITZOU2025] {(Ranked second)}\newline
}

%-------------------------------------------------------------------------------
% Honors and Awards
%-------------------------------------------------------------------------------
\label{sec:HonorsAndAwards}
\section{Honors and Awards}

\label{HA:ROTARY2025}
\cvitem{Nov 2025}
{
\textbf{""Evangelos Kastamonitis" Postgraduate Scholarship"\newline}
Issued by: \textbf{Rotary Club Corfu}\newline
Scholarship awarded by Rotary Club Corfu to one Corfiot postgraduate student based on their academic performance, economic situation, and activity. It lasts until graduation if the student maintains their performance. This was the very first postgraduate scholarship to be offered by the Rotary Club of Corfu.
}

\label{HA:KARAMITZOU2025}
\cvitem{Jul 2025}
{
\textbf{"Ranked second among my year's admission students, "Elisabeth Karamitzou" Award"\newline}
Issued by: \textbf{University of Crete (UoC)}\newline
An annual award given to the top three students of each department of the University of Crete who completed their studies within the prescribed period of study, and based on their grades. I was ranked second among my year's admission students with a grade of 9.57/10.
}

\label{HA:EPFL2025}
\cvitem{Jan 2025}
{
\textbf{"Top 13\%, Summer@EPFL Internship Program"\newline}
Issued by: \textbf{Ecole Polytechnique Federale de Lausanne (EPFL)}\newline
I was shortlisted and ranked among the top 13\% of all 5900 applicants worldwide in the Summer@EPFL Internship Program of the Ecole Polytechnique Federale de Lausanne, based on academic performance and curriculum vitae (CV). (Final selection not awarded.)
}

\label{HA:DEPROFOIT}
\cvitem{Sep 2025, 2024}
{
\textbf{"DEPROFOIT Distinction"\newline}
Issued by: \textbf{Computer Science Department, University of Crete}\newline
Praise awarded by the Department of Computer Science, University of Crete for successfully taking on a teaching assistantship during the academic year. The related courses were CS252: Object-Oriented Programming, CS109: English II, and CS209: English IV for both awards.
}

\label{HA:HIAS2024}
\cvitem{Mar 2024}
{
\textbf{"Eighth place, Nicholas and Robert Askounes Ashford Educational Scholarship"\newline}
Issued by: \textbf{Hellenic Institute of Advanced Studies (HIAS)}\newline
I was ranked 8th in Greece in the Nicholas and Robert Askounes Ashford Educational Scholarship of the Hellenic Institute of Advanced Studies, based on academic performance and research proposal (final selection not awarded).
}

\label{HA:ROTARY2023}
\cvitem{Nov 2023}
{
\textbf{""Evangelos Kastamonitis" Undergraduate Scholarship"\newline}
Issued by: \textbf{Rotary Club Corfu}\newline
Scholarship awarded by Rotary Club Corfu to one Corfiot undergraduate student based on their academic performance, economic situation, and activity. Lasts until graduation if the student maintains their performance.
}

\label{HA:FORTH2023}
\cvitem{Jul 2023}
{
\textbf{"FORTH Undergraduate Student Scholarship"\newline}
Issued by: \textbf{Institute of Computer Science (ICS), Foundation for Research and Technology - Hellas (FORTH)}\newline
Scholarship awarded by the Information Systems Laboratory (ISL), FORTH to undergraduate students of the lab. Lasts while the student is active and productive on ISL and until graduation.
}

%-------------------------------------------------------------------------------
% Contests
%-------------------------------------------------------------------------------
\label{sec:Contests}
\section{Contests}

\label{HA:CONTEST:5thPlaceMentorMindFu}
\cvitem{2-3 Oct 2025}
{
\textbf{5th Place, MentorMind (FuturEd AI Hackathon)\newline}
Issued by: \textbf{Computer Science Department, University of Crete}\newline
Designed and implemented an AI Mentor platform in 24 hours during the FuturED AI Hackathon. The Mentor could provide assistance and suggestions to the user for academic issues based on their preferences, ranging from structured options like professors and topics, to unstructured free text, based to the department schedule and study guide. The frontend was implemented in ReactJS and MaterialUI, the backend was a RAG implementation in JavaScript, the communication was based upon services architecture, and the text from the department documents was extracted using AI methods. The project was ranked as 5th out of the 16 projects presented, with a near-tie for 4th place.
}

\label{HA:CONTEST:2ndplaceTriangleMEM3}
\cvitem{18 Jun 2024}
{
\textbf{2nd place, Triangle (MEM-343: Entrepreneurship and Innovation course)\newline}
Issued by: \textbf{Department of Mathematics and Applied Mathematics, University of Crete}\newline
The business idea Triangle got second place in the open-to-the-public business idea presentation event in the context of the Innovation and Entrepreneurship course. The business ideas presented were evaluated by a five-member jury, with Triangle taking - in a tie - 2nd place.
}

\label{sec:Publications}
\section{Publications}

\label{PUB:P3}
\cvitem{P3}
{Sophia Sideri, Emmanouil Patronakis, Evangelos Nikiforos, Isidoros Chatzichrysos, Apostolos Baniotis, \textbackslash\{\}textbf\{Valantis Zervos\}, Stavros Tzormpatzakis, Michalis Saridakis, Iosif Oikonomakis, Michalis Mountantonakis, Pavlos Fafalios and Yannis Tzitzikas},
To Automate or not to Automate the Transcription of Ancient Earthquakes: Toward a Global Knowledge Graph about Ancient Earthquakes
(2025, ijckg 2025)
}

\label{PUB:P2}
\cvitem{P2}
{Iordanis Sapidis, \textbackslash\{\}textbf\{Valantis Zervos\}, Michalis Mountantonakis, and Yannis Tzitzikas},
Interactive and Provenance-aware Search and QA over Documents using LLMs, RAG and Knowledge Graph Verbalization
, TPDL 2025 \textbf{Bachelor Thesis}
}

\label{PUB:P1}
\cvitem{P1}
{Yannis Marketakis, Michalis Mountantonakis, Pavlos Fafalios, \textbackslash\{\}textbf\{Valantis Zervos\}, Arne Langlet, Anton Ellenbroek, Kim J. Friedman, and Yannis Tzitzikas},
Analysis of Large Numbers of Scientific Papers: A Case Study on Finding the Focus of Ecosystem Restoration Intervention
(2024, under preparation, to submit at Ecological Modelling Journal)
}

%-------------------------------------------------------------------------------
% Technical Reports
%-------------------------------------------------------------------------------
\label{sec:TechnicalReports}
\section{Technical Reports}

\label{TR:TR1}
\cvitem{TR1}
{Yannis Marketakis, Yannis Tzitzikas, Pavlos Fafalios, Michalis Mountantonakis, and \textbackslash\{\}textbf\{Valantis Zervos\}},
Analysis of the 'focus' and 'sentiment' of restoration interventions in the aquatic domain, delivered to FAO, Sep 2024
}

%-------------------------------------------------------------------------------
% Software Projects
%-------------------------------------------------------------------------------
\label{sec:ResearchProfessionalProjects}
\section{Research/Professional Software Projects}
\href{https://github.com/VZervos}{GitHub: \textcolor{blue}{https://github.com/VZervos}}
\\[1em]

\label{RPP:SP2}
\cvitem{SP2}{
\textbf{FAO Restoration Analysis: GIS} \newline
Duration: Jul 2024 - Sept 2024 \newline
Host: FORTH, Food and Agriculture Organization (FAO-UN) \newline
My Role: \textbf{Full-Stack Developer} \newline
Designed and implemented a Geographical Information System (GIS) platform as an extension of the paper "Valantis Zervos, Iordanis Sapidis, Michalis Mountantonakis, and Yannis Tzitzikas, Evaluation of RAGs over Scientific Literature (case study: FAO Ecosystem Restoration bibliography)" which takes as input a data file (.mra file) from the tool presented in the paper and shows its contents on a live map. Implemented using ReactJS, MaterialUI and ArcGis.
}

\label{RPP:SP1}
\cvitem{SP1}{
\textbf{EKT WorkFun+} \newline
Duration: Jul 2023 - Jan 2024 \newline
Host: FORTH, National Documentation and Electronic Content Centre of Greece (EKT) \newline
My Role: \textbf{Full-Stack Developer} \newline
Designed and implemented a statistics component with data visualization (bars, pies) using ReactJS and MaterialUI. Developed a barcode generation service using Java for PDF outputs.
}

%-------------------------------------------------------------------------------
% Course Projects
%-------------------------------------------------------------------------------
\label{sec:CourseProjects}
\section{Course Projects}
\href{https://github.com/VZervos}{GitHub: \textcolor{blue}{https://github.com/VZervos}}
\\[1em]

\label{CP:CP7}
\cvitem{\label{CP:CP7} CP7}{
\textbf{Analysis, Design, Implementation and Evaluation of an E-Sports Platform} \newline
Duration: Apr 2025 – May 2025 \newline
Analyzed and designed a platform for hosting E-Sports events and their content, as a CS351: Information Systems Analysis and Design course project. The platform was partially - as requested - implemented, and fully evaluated. The implementation was made using React-TS, Docker, HTML5/CSS, and Material-UI. The evaluation was made using W3 Validator, Wave, Lighthouse and Heuristics.
}

\label{CP:CP6}
\cvitem{\label{CP:CP6} CP6}{
\textbf{Information Retrieval System (IRS)} \newline
Duration: Apr 2025 – May 2025 \newline
Implemented an information retrieval system that can index and answer queries on a corpus of 2.5GB consisting of medical research articles, as a CS463: Information Retrieval Systems course team project. The system was also evaluated using various metrics. The implementation was made using Java and Python.
}

\label{CP:CP5}
\cvitem{\label{CP:CP5} CP5}{
\textbf{E199} \newline
Duration: Dec 2024 – Jan 2025 \newline
Created a web platform for the Fire Department allowing incident submission \& management, user sessions, communication, and more, using HTML, CSS, JavaScript, OpenLayers Maps, Bootstrap, JQuery, and other libraries as a CS359: Web Development course project.
}

\label{CP:CP4}
\cvitem{\label{CP:CP4} CP4}{
\textbf{Alpha Compiler} \newline
Duration: Feb 2024 – Jun 2024 \newline
Created a compiler for the Alpha programming language using C, Flex, and Bison. The compiler compiled Alpha code to execute on an Alpha Virtual Machine.
}

\label{CP:CP3}
\cvitem{\label{CP:CP3} CP3}{
\textbf{Business Plan: Triangle} \newline
Duration: Apr 2024 – Jun 2024 \newline
Researched, created, and presented the business plan Triangle during a public pitch event. Ranked second place in a competitive evaluation.
}

\label{CP:CP2}
\cvitem{\label{CP:CP2} CP2}{
\textbf{Vehicle Rental Management System} \newline
Duration: Dec 2023 – Jan 2024 \newline
Built a complete rental management system for businesses using Java and SQL. The system supported client registration, vehicle tracking, and payment management.
}

\label{CP:CP1}
\cvitem{\label{CP:CP1} CP1}{
\textbf{Stratego: Ice vs Fire} \newline
Duration: Dec 2022 \newline
Developed a 2D multiplayer strategy game in Java, featuring various game modes and intuitive user controls.
}

%-------------------------------------------------------------------------------
% Work Experience
%-------------------------------------------------------------------------------
\label{sec:WorkExperience}
\section{Work Experience}

\label{WE:INGENIUM2025}
\cvitem{Nov 2025 - Present}
{
\textbf{Member of the INGENIUM Student Board\newline}
Representative of the University of Crete\newline
Work with the other student representatives chosen from INGENIUM universities on discussing regulations, projects, and other activities involving students and the partner universities.
}

\label{WE:TA2023}
\cvitem{Oct 2023 - Present}
{
\textbf{University Teaching Assistant (DEPROFOIT)\newline}
Computer Science Department, University of Crete, Heraklion, Greece\newline
Responsibilities: Corrected and designed assignments, conducted office hours, presented tutorials, organized and managed course (along with Professor), and course platforms for the courses::
\begin{itemize}
    \item CS252: Object-Oriented Programming (Fall 2023, 2024, 2025) [\(\sim \)360 students]
    \item CS109: English II (Spring 2024, Spring 2025) [\(\sim \)200 students]
    \item CS209: English IV (Spring 2024, Spring 2025) [\(\sim \)220 students]
\end{itemize}
}

\label{WE:FORTH}
\cvitem{Jul 2023 - Present}
{
\textbf{Graduate Researcher at FORTH\newline}
FORTH-Institute of Computer Science, Heraklion, Greece\newline
Previously: Undergraduate Fellow, until July 2025
Indicative work:
\begin{itemize}
    \item Contributed to various research projects as well as an industrial project [\hyperref[RPP:SP1]{SP1}, \hyperref[PUB:P3]{P3}]
    \item Developed tools for:
    \begin{itemize}
        \item Text extraction from PDF files.
        \item Bibliographic analysis on .bib files.
        \item Geographic data visualization on a live map platform.
    \end{itemize}
    This work was conducted using Java, PDFBox, ReactJS, MaterialUI, and ArcGIS in the context of a research project for FAO (Food and Agriculture Organization of the United Nations), running from November 2023 to September 2024. [\hyperref[RPP:SP2]{SP2}, \hyperref[PUB:P1]{P1}].
    \item Researched the impact of Knowledge Graphs and Large Language Models (LLMs) on Retrieval-Augmented Generation (RAG) systems. [\hyperref[PUB:P2]{P2}]
    \item And more...
\end{itemize}
}

%-------------------------------------------------------------------------------
% Schools & Seminars
%-------------------------------------------------------------------------------
\label{sec:SchoolsSeminars}
\section{Schools \& Seminars}

\label{SS:CCI2025}
\cvitem{2025}{
\textbf{CCI Summer School \newline}
\textbf{21 - 25 Jul 2025, FORTH, Heraklion, Greece} \newline
CIDOC CRM Interoperability and Applications \newline
Attended the Summer School on CIDOC CRM (July 2025, FORTH-ICS, Heraklion, Crete), part of the Digital Humanities programme. Received training on conceptual modeling, interoperability, and applications of the CIDOC CRM ontology. Participated in hands-on sessions on data transformation and knowledge graph construction. Explored the use of CIDOC CRM in cultural heritage documentation and AI-supported workflows.
}

\label{SS:INGENIUM2025}
\cvitem{2025}{
\textbf{INGENIUM Junior Winter School 2025 \newline}
\textbf{9 - 14 Feb 2025, Xamk University, Mikkeli, Finland} \newline
From Idea to Disruption: Transforming Visions into Innovations \newline
School on entrepreneurial skills, design thinking, multicultural teamwork, and communication skills by solving real-life stakeholders' challenges and cases. The main project was to solve a real-life case problem provided by the stakeholder and develop and present it as a business idea in a 10-minute pitch.
}

%-------------------------------------------------------------------------------
% Academic Volunteering
%-------------------------------------------------------------------------------
\label{sec:AcademicVolunteering}
\section{Academic Volunteering}

\label{AV:RESEARCHERNIGHT}
\cvitem{2025}
{
Researcher's Night \newline
26 Sept 2025\newline
Assistant/Guide at FORTH
}

\label{AV:TOTTCONF}
\cvitem{2025}
{
"Developing Faculty members' Pedagogical Acuity" ToTT 1st International Faculty Development and Higher Education Conference \newline
23 May - 25 May 2025\newline
Tech Support at Computer Science Department, University of Crete
}

\label{AV:SCHOOLVISITCSD}
\cvitem{2025, 2024}
{
University Open Week for Schools \newline
29 Jan - 2 Feb 2024, 3-7 Feb 2025\newline
Assistant/Guide at Computer Science Department, University of Crete
}

\label{AV:CAREERFAIRUOC}
\cvitem{2025, 2024, 2023}
{
Career Fair UoC \newline
Nov 2025, Mar 2023, Apr 2024\newline
Tech Support at Mathematics and Applied Mathematics Department (2025, 2023), and Chemistry Department (2024), University of Crete
}

%-------------------------------------------------------------------------------
% Other Volunteering
%-------------------------------------------------------------------------------
\label{sec:OtherVolunteering}
\section{Other Volunteering}

\label{OV:TRADITIONALDANCEEVENT}
\cvitem{2023 - 2025}
{
Event Organizer: Traditional Dance Performance event \newline
August 2023, 2024, 2025 \newline
Fully organized a traditional dance performance event and taught traditional dancing to a group of about 10 students at the central square of Kynopiastes as part of the village's 15th August events
}

\label{OV:CULTURALINTERVENTION}
\cvitem{2023 - 2025}
{
Cultural Intervention Program \newline
Nov 2023 - Apr 2024, Nov 2024 - May 2025 \newline
Presenter at Directorate of Elementary Education of Heraklion
}

\label{OV:SALESREPRESENTATIVE}
\cvitem{2022 - Present}
{
Sales Representative \newline
July and August of 2022 - 2025 \newline
Promoted the lottery/giveaway, held by the Philarmonic Orchestra of Kynopiastes, face-to-face to stores and people on the street, and sold 100 lottery coupons on average each time.
}

%-------------------------------------------------------------------------------
% Languages
%-------------------------------------------------------------------------------
\label{sec:Languages}
\section{Languages}
\cvitem{\textbf{Greek} }{Native}
\cvitem{\textbf{English} }{Proficient (C2, ECPE Certification)}
%-------------------------------------------------------------------------------
% Hobbies and Interests
%-------------------------------------------------------------------------------
\label{sec:HobbiesInterests}
\section{Hobbies and Interests}
\cvitem{\textbf{Traditional Greek Dancing}}{Teacher, group leader, and performer in national and local shows.}
\cvitem{\textbf{Music}}{Musician (Percussion) in the Philarmonic Orchestra of Kynopiastes.}
\cvitem{\textbf{Game Dev}}{Developed and managed Minecraft game servers.}
\cvitem{\textbf{Acting}}{Participant in a local amateur troupe.}
%-------------------------------------------------------------------------------
% References
%-------------------------------------------------------------------------------
\label{sec:References}
\section{References}

\label{REF:TZITZIKAS}
\cvitem{\textbf{Yannis Tzitzikas}} {
Professor at University of Crete,\newline
Affiliated Researcher at ICS-FORTH,\newline
Deputy Chair at Computer Science Department, University of Crete\newline
tzitzik@ics.forth.gr
}

\label{REF:MAGOUTIS}
\cvitem{\textbf{Kostas Magoutis}} {
Associate Professor at University of Crete,\newline
Collaborating Researcher at ICS-FORTH,\newline
Chair at Computer Science Department, University of Crete\newline
magoutis@ics.forth.gr
}

\label{REF:RIZOPOULOU}
\cvitem{\textbf{Noni Rizopoulou}} {
Professor at University of Crete\newline
nrizop@csd.uoc.gr
}

\label{REF:MARKETAKIS}
\cvitem{\textbf{Yannis Marketakis}} {
Senior Research Engineer and Technical Head of CCI at ICS-FORTH\newline
marketak@ics.forth.gr
}

\label{REF:KRITSOTAKIS}
\cvitem{\textbf{Vangelis Kritsotakis}} {
Software Engineer at ICS-FORTH\newline
vkrits@ics.forth.gr
}

\label{REF:SAMPSONIDIS}
\cvitem{\textbf{Dimitris Sampsonidis}} {
Career Counsellor at University of Crete,\newline
Co-Founder at Youth Crete (Region's of Crete NGO)\newline
d.sampsonidis@uoc.gr
}

\end{document}
